### 2022-05-31 article.tex
Better table with recommendations

>>>>

\begin{table}[h]
  \begin{tabular}{lp{9cm}}
    Type of code  & Recommendation \\
    \hline
    No code       & Disallow papers that do not supply code publicly \\
    Raw code      & Don't publish raw code as text, instead, host it on a code hosting website \\
    Hosted code   & Add CI. Use standarized badges for build status and code coverage. 
                    Provide for a standarized way to link between paper and code host \\
    Runnable code & Provide website to upload containers with proper annotation.
                    Provide for a standarized way to link between container, paper and code repository
  \end{tabular}
  \caption{Recommendations described in this paper}
  \label{tab:recommendations}
\end{table}
